Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-07-22 text/manuscript-full-KS.qmd
add College Board 2023 PDF

We assigned each census tract to a College Board Geomarket, which we constructed through manual digitization of maps published by The College Board in 2023 marketing materials promoting their Enrollment Planning Service (EPS) software products. Specifically, we georeferenced the College Board’s Geomarket maps by overlaying PDF images onto spatial coordinates aligned with census tract boundaries. We then extracted vector data by manually tracing the Geomarket boundaries and generating individual shapefiles for each Geomarket. For instance, @fig-geomarket-methods shows The College Board's map of Geomarkets in the Chicago metropolitan area on the left and our created shapefiles on the right.

>>>>

We assigned each census tract to a College Board Geomarket, which we constructed through manual digitization of maps published by The College Board in 2023 marketing materials promoting their Enrollment Planning Service (EPS) software products [@collegeboard_connections_geographies]. Specifically, we georeferenced the College Board’s Geomarket maps by overlaying PDF images onto spatial coordinates aligned with census tract boundaries. We then extracted vector data by manually tracing the Geomarket boundaries and generating individual shapefiles for each Geomarket. For instance, @fig-geomarket-methods shows The College Board's map of Geomarkets in the Chicago metropolitan area on the left and our created shapefiles on the right.
